\documentclass[letterpaper]{article}

%% Language and font encodings
\usepackage[english]{babel}
%\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage{todonotes}

%% Sets page size and margins
\usepackage[letterpaper,top=1in,bottom=1in,left=1in,right=1in,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{outlines}
%\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

%% Overwrite title macro

\makeatletter
    \def\@maketitle{%
  \newpage
  \null
  \vskip 2em%
  \begin{center}%
  \let \footnote \thanks
    {\Large \@title \par}%
    {\Large \@author \par}%
    {\large \@date \par}%
  \end{center}%
  \par
  \vskip 1.5em}
\makeatother

%% make table spacing less awful

\def\arraystretch{1.25}%  1 is the default, change whatever you need

%% Title

\title{\textbf{EE106A/206A / BIOE125}}
\author{Final Project Proposal Template} %% CHANGE THIS TO YOUR PROJECT TITLE
\date{Fall 2018}


%% Document

\begin{document}
\maketitle

\section{Contact Information}


\begin{tabular}[h]{l|l|l}
\textbf{Name} & \textbf{SID} & \textbf{Email} \\
\hline
Xiomara Gonzalez & 26346976 & xiomarag@berkeley.edu \\
Jiayi Chen & 3033318654 & jiayi\_chen@berkeley.edu \\
\end{tabular}

\section{Abstract}


\section{Project Description}

Our goal for this project is to use a Baxter robot to classify items into different categories depending on their shape and corresponding attributes.\medskip\\
First, we will have basic shapes like triangles, circles, and rectangles placed on a surface (our backup plan due to potential difficulties in precise classification is to mark the surface and/or item by an AR tag). Baxter will sense the items by using the camera attached to it to take a picture of the area it will scan. Since the possibility that the image will contain regions we do not want to focus on, we have to ensure those regions are removed. The image collected will serve as input for an algorithm that will apply image processing and edge detecting filters (ie: Canny Edge Detection, Gaussian blurring) in order to better detect the shapes. \smallskip\\Second, a template matching algorithm will take a gray-scale version of the filtered image and multiple pre-generated templates for each of the shapes we want to sort through. The algorithm will detect the shapes on the surface and compute the centroid of corners with some threshold (this would serve as information to compute Baxter's target pick-up location).\smallskip\\Third, we can then apply inverse kinematics to control Baxter's gripper to go to the desired location and pick up the item. One safety issue that could occur is Baxter's arm damaging other items along the path to the target drop-off location, so we have to ensure the path it is taking will not interfere with surrounding objects. Each shape will have a final target location and Baxter will place it there.\medskip\\
We think that this project is particularly interesting due to its wide variety of real life applications. From the projects that were shown to us from previous years, we saw that a lot of them used AR tags, the camera from the Kinect, and the pre-built libraries in their projects. So, several of the approaches that we are interested in testing have been tried out before, however the applications that they were used towards differed from what we have in mind for our project. One of the applications that our Baxter classification system can be used towards is human assistance, especially for people who are visually impaired or incapacitated. The open-endedness of this project allows us to add complexity to it if possible as the classification of specific shapes can be turned into classification of an entire collection of objects in a household. 


The template matching algorithm can be adjusted to use multiple strategies to be able to detect the shapes. We were thinking about using fast, normalized cross-correlation to find instances of the templates in the image that Baxter takes. We would allow for multiple peaks to pass through, so we can take into consideration the case where there can be multiple shapes of the same kind. Another thing we can do is apply image filters (Gaussian blurring, bilateral filtering, etc..) to help the template matching algorithm get better results.\medskip\\
Implementing a basic classification model for Baxter can have many real life applications. One that stands out is using this type of system to find common, everyday life objects for people that are sightless or incapacitated. Other applications can include sorting packages in warehouses and organizing products in store shelves.

\section{Tasks}
\begin{outline}[enumerate]

\1 \textbf{Build the robot.} We will be using the Baxter robot in the lab for our project. 

\1 \textbf{Code the robot.} We will be using Python for the scripts that we need to create. There are also outside libraries that could be useful to our project, including OpenCV and Scikit-image, that offer the filtering algorithms and object detection functions that we are interested in. Since these are pre-built and generalized, we expect to have to customize the functions towards our project or add some sort of adjustments to them. The algorithms that we have planned to use will be tested to see which one works better for our project, as a result, we will have to create several scripts with different approaches.      
\2 \textbf{Shape detection.} This script will be responsible for taking the image that Baxter takes and running an algorithm that is able to detect shape edges and corners.
\3 \textbf{Canny Edge Detection.} One approach we can take is using Canny Edge Detection to isolate each of the shapes' edges. We would have to find a way to just consider edges that have a high probability of being a shape's edge and not something like the edge of a table.
\3 \textbf{Corner Detection.} Another approach we can take in addition to edge detection is having a script that will estimate a shape's corners depending on the outline provided. With this we can have a better idea of how much Baxter's grip is expected to open and get a sense of how much it needs to close.
\3 \textbf{Center detection.} In order to find a certain shape's center, we can use peak finding      
\2 \textbf{Template matching.} This script will be responsible for taking a segmented image (our definition of "segmentation" is an image that only contains shape outlines, anything else should be considered background) and detecting which shape an outline corresponds to. 
\2 \textbf{Path planning.} Using MoveIt, we will compute inverse kinematics solutions for Baxter's arm. For this part specifically, we expect that we will have to spend more time trying to see what works best. Since the MoveIt solutions are non-deterministic, we can add specific constraints to ensure the paths that the arm takes are not too extraneous.    

\end{outline}

\section{Milestones}
\begin{itemize}
\item 10/28: Find all of the OpenCV and Scikit-image functions that we want to use for our project, familiarize ourselves with the libraries and review past lab material that we might need 
\item 11/11: Have basic scripts working with sample images that we take ourselves. Find which functions work best and finalize what we will use for the final version of the scripts 
\item 11/18: Integrate the robot and code together using ROS nodes, topics, and additional communication methods
\item 12/02: Have a fully functioning project that meets this project proposal
\item 12/02 - presentation: Tweak code and try to optimize parts of project
\end{itemize}

\section{Assessment}
We will test our project by setting up different configurations and making sure that the robot is able to classify the objects consistently. Success to us would mean that all objects placed on the surface should be placed in their corresponding target locations after correctly locating them. I think that the goals we have proposed here are realistic and intuitively straightforward to understand, however complications could arise when we integrate the code and hardware, so we will use our back-up approaches if necessary. Some reach goals that we have is to add complexity to the objects we are able to detect (ie: cell phone, cups, pencils, wires). 

\section{Team Member Roles}
\begin{itemize}
  \item Xiomara will be in charge of the shape detection scripts (edge detection and template matching). She has done research that focuses on image segmentation and a lot of the concepts she uses there are applicable to the image processing techniques that are needed for this kind of object detection.
  \item 
\end{itemize}

\section{Bill of Materials}
\subsection{Use of Lab Resources}

\vspace{1em}

\begin{tabular}[h]{l|l}
\textbf{Item} & \textbf{Quantity} \\
\hline Baxter(w/ parallel gripper) & 1 \\Camera & 1 \\
\end{tabular}

\subsection{Other Robotic Platforms}
None available.

\subsection{Items for Purchase}

\vspace{1em}

\begin{tabular}[h]{l|l|l|l|l}
\textbf{Item} & \textbf{Quantity} & \textbf{Price} & \textbf{Website} & \textbf{Justification} \\
\hline
 & & & & \\
 & & & & \\
\end{tabular}

\section{Other}

\begin{itemize}
\item ROS packages you'll need (with pointers to relevant websites); 
\item preliminary code structure/skeleton; and 
\item mechanical designs/drawings/sketches of your project.
\end{itemize}

\end{document}
